---
title: "Ramen ratings"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
```

This was a short analysis I did using an old TidyTuesday dataset for ramen ratings. It was an enjoyable experience, as I figured out how to graph data on maps! These were the resulting graphs.

```{r}
library(tidyverse)
library(dplyr)
library(readr)
library(ggplot2)
library(rgeos)
library(mapproj)
library(modelr)
library(knitr)
library(sjPlot)

ramen <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-04/ramen_ratings.csv") %>%
  mutate(
    variety = factor(variety),
    style = factor(style)
  ) %>% na.omit()

```

## Top 25 ramen brands by review number:

It looks like Nissin was the winner here.

```{r}
ramen %>% 
  group_by(brand) %>% 
  summarise(reviews = sum(review_number))%>% 
  arrange(desc(reviews)) %>% 
  top_n(25) %>% 
  ggplot(aes(brand, reviews, fill = brand))+
  geom_col()+
  theme(axis.text.x = element_text(angle = 270))
```

## Top ramen brand for each country by review count

Unfortunately, due to missing data I could only visualize the top brands for their respective origin countries.

```{r, fig.width= 12, fig.height= 6.5}
world_map <- map_data("world")

x <- ramen %>% 
  group_by(country, brand) %>% 
  summarise(reviews = sum(review_number)) %>% 
  arrange(desc(reviews)) %>% 
  top_n(1) 

top_brand <- x[,1:2]

plot1 <- full_join(top_brand, world_map, by = c("country" = "region"))

ggplot(plot1, aes(long, lat, group = group))+
  geom_polygon(aes(fill = brand))+
  labs(x = "Longitude",
       y = "Latitude",
       title = "Top ramen brand in origin country",
       subtitle = " according to review count")

```

## Top ramen brands by average rating

MyKuali wins this round. I filtered to only include brands with over 100 reviews to root out brands with lower review counts who had all 5-stars.

```{r}
ramen %>% 
  group_by(brand) %>% 
  summarise(average_rating = mean(stars),
            reviews = sum(review_number))%>% 
  filter(reviews > 100) %>% 
  arrange(desc(average_rating))%>% 
  top_n(25) %>% 
  ggplot(aes(brand, average_rating, fill = brand))+
  geom_col()+
  theme(axis.text.x = element_text(angle = 270))+
  labs(x = "Brand",
       y = "Average rating")


```

## Top ramen brands in their origin countries according to average rating

There don't appear to be many differences from the map using brands sorted by review count.

```{r, fig.width=12, fig.height=6.5}
top_brand_rating <- ramen %>% 
  group_by(country, brand) %>% 
  summarise(average_rating = mean(stars),
            reviews = sum(review_number))%>% 
  filter(reviews > 100) %>% 
  arrange(desc(average_rating))%>% 
  top_n(1)

top_brand_rating <- top_brand_rating[,1:2]

plot2 <- full_join(top_brand_rating, world_map, by = c("country" = "region"))

ggplot(plot2, aes(long, lat, group = group))+
  geom_polygon(aes(fill = brand))+
  labs(x = "Longitude",
       y = "Latitude",
       title = "Top ramen brand in origin country",
       subtitle = " according to average rating",
       caption = "(taking brands with over 5000 reviews)")
```


## Top ramen style by country (according to review count)

Finally, I looked at preferred ramen style.

```{r, fig.width=9, fig.height=6}
top_style <- ramen %>% 
  group_by(country, style) %>% 
  summarise(reviews = sum(review_number))%>%
  arrange(desc(reviews)) %>% 
  top_n(1)

top_style <- top_style[,1:2]  

plot3 <- full_join(top_style, world_map, by = c("country" = "region"))

ggplot(plot3, aes(long, lat, group = group))+
  geom_polygon(aes(fill = style))+
  labs(x = "Longitude",
       y = "Latitude",
       title = "Top ramen style in orgin country",
       subtitle = " according to review count")
```

## A couple of linear regressions.

Finally, I ran a couple regressions, which weren't very accurate, as indicated by the low adjusted R-squared values.

```{r}
topramenbrand <- ramen %>% 
  group_by(brand) %>% 
  summarise(reviews = sum(review_number)) %>% 
  arrange(desc(reviews)) %>% 
  top_n(25) %>% 
  pull(brand)

topramen <- ramen %>% 
  filter(brand %in% topramenbrand)

lm <- lm(review_number ~ style + brand, data = topramen )

topramenbrand2 <- ramen %>% 
  group_by(brand) %>% 
  summarise(average_rating = mean(stars),
            reviews = sum(review_number))%>% 
  filter(reviews > 100) %>% 
  arrange(desc(average_rating))%>% 
  top_n(25) %>% 
  pull(brand)

topramen2 <- ramen %>%
  filter(brand %in% topramenbrand2) %>% 
  mutate(brand = factor(brand))

lm2 <- lm(review_number ~ brand, data = topramen2)

tab_model(lm, lm2, p.style = "stars", show.ci = FALSE)
```